A Large and Variable Leading Tail of Helium in a Sub-Saturn Undergoing Runaway Inflation

### 2023-06-26 paper/paper1/ms.tex
Improved discussion about the mass constraint

We conducted orbit fitting via precision radial velocity (PRV) measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}, but without a joint Gaussian Process modeling procedure \citep{2023ApJ...950..162T}.  Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.  The HPF points exhibited an RV jitter of $\sim164\;\ms$, a few times larger than the typical Keck HIRES measurements.  So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.  The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \kms.  The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the radius would exceed the Hill radius (Roche lobe overflow).  Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint, but consistent with broadly Saturn-mass planets.  Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.  Hypothetically, a truly Roche lobe overflow planet could be consistent with the available data, so our constraint could be considered an upper limit.

>>>>

We conducted orbit fitting via precision radial velocity (PRV) measurements following the procedures described in \citet{2021AJ....161..173T} and updated for joint lightcurve and RV fits \citep{2022AJ....163..225T}, but without a joint Gaussian Process modeling procedure \citep{2023ApJ...950..162T}.  Here we included the new TESS lightcurves and the existing Keck HIRES points reported in Table 3 of \citet{2017AJ....153..211Z}.  The HPF points exhibited an RV jitter of $\sim164\;\ms$, a few times larger than the typical Keck HIRES measurements.  So even though the HPF points were more numerous, their marginal value for RV orbit determination was subdued owing to the lower RV information content in the near-IR for this relatively rapidly rotating F star.  The period and $T_0$ were fixed from the \emph{TESS} transits, and we assume a circular orbit with $K>10$ \kms.  The semiamplitude prior acts as a mass constraint, excluding planets with masses so low that the radius would exceed the Hill radius (Roche lobe overflow).  Figure \ref{fig:RVfit} shows the fitted RV semiamplitude $K=33_{-15}^{+21}$ \ms, a relatively weak constraint, but consistent with broadly Saturn-mass planets.  Table \ref{tabOrbit} lists the revised properties, with minor differences from the existing values.  The semiamplitude prior accounts for the apparent improvement in the mass constraint.  Hypothetically, a truly Roche lobe overflow planet could be consistent with the available data, so our mass constraint could be considered an upper limit.
